%%% List of published volumes Acta Philosophica Gothoburgensia
%%% Check with the series editors to make sure all volumes are on the list.
%
% To add your own volume at the end of the list, please use the following format:
% \item Name Surname.\enspace\textit{Title: Subtitle}. \mbox{G\"oteborg} Year
% 
% If an entry is ever split across columns, add the following line before that entry.
% \columnbreak
%
% If an entry is ever split across pages, add the following line before that entry.
% \pagebreak
%
% If either of these leads to bad spacing of a column, try prepending the line
% \vfill\null

\documentclass[fontsize=14pt,
               paper=297mm:210mm,
               twoside,
               pagesize=pdftex,
               DIV=calc
]{scrbook}

%%% Available options: draft/final
\usepackage[final]{ACTA}

\usepackage{multicol}
 

\usepackage[protrusion=true, factor=1000]{microtype}

\raggedcolumns
\begin{document}
\newgeometry{left=25mm,right=25mm,top=30mm,bottom=30mm}
\fontsize{12}{15}\selectfont
\thispagestyle{empty}
\selectlanguage{UKenglish}


\pagestyle{empty}


\begin{center}
\addfontfeature{SmallCapsFeatures={Numbers=OldStyle}} % Old style number look better in the small caps headline
\textsc{acta philosophica gothoburgensia}

\textsc{issn 0283-2380}

\vspace{\baselineskip}
 Editors: Bengt Br\"ulde, Graham Leigh, Anna-Sofia Maurin and Christian Munthe
\vspace{\baselineskip}

Subscriptions to the series and orders for individual copies are sent to:

\textsc{acta universitatis gothoburgensis}

Box 222, 405 30 G\"oteborg, Sweden

\url{acta@ub.gu.se}
\end{center}
\raggedcolumns

\setlength\columnsep{20pt}
\begin{multicols*}{2}
\newcounter{volumes}
\newenvironment{Volumes}
{\begin{list}{\arabic{volumes}. }{\usecounter{volumes}%
\setlength{\labelsep}{0pt}%
\setlength{\leftmargin}{0pt}%
\setlength{\labelwidth}{0pt}%
\setlength{\listparindent}{0pt}%
\setlength{\itemsep}{6pt}%
\setlength{\topsep}{0pt}%
\setlength{\parsep}{0pt}}}%
{\end{list}}
\noindent Previous publications:

\begin{Volumes}
\item Mats Furberg, Thomas Wetterstr\"om \& Claes \AA{}berg (eds.).\enspace\textit{Logic and abstraction: Essays dedicated to Per Lindstr\"om on his fiftieth birthday.} \mbox{G\"oteborg} 1986

\item Staffan Carlshamre.\enspace\textit{Language and time: An attempt to arrest the thought of Jacques Derrida}. \mbox{G\"oteborg} 1986

\item Claes \AA{}berg (ed.).\enspace\textit{Cum grano salis: Essays dedicated to Dick A.~R.~Haglund}. \mbox{G\"oteborg} 1989

\item Anders Tolland.\enspace\textit{Epistemological relativism and relativistic epistemology}. \mbox{G\"oteborg} 1991

\item Claes Stranneg\aa{}rd.\enspace\textit{Arithmetical realizations of modal formulas}. \mbox{G\"oteborg} 1997

\item Bengt Br\"ulde.\enspace\textit{The Human Good}. \mbox{G\"oteborg} 1998

\item Eva Mark.\enspace\textit{Sj\"alvbilder och jagkonstitution}. \mbox{G\"oteborg} 1998

\item May Torseth.\enspace\textit{Legitimate and Illegitimate Paternalism in Polyethnic Conflicts}. \mbox{G\"oteborg} 1999

\item Christian Munthe.\enspace\textit{Pure Selection: The Ethics of Preimplantation Genetic Diagnosis and Choosing Children without Abortion}. \mbox{G\"oteborg} 1999

\item Johan M\aa{}rtensson.\enspace\textit{Subjunctive Conditionals and Time: A Defense of a Weak Classical Approach}. \mbox{G\"oteborg} 1999

\item Claudio M.~Tamburrini.\enspace\textit{The ``Hand of God''? Essays in the Philosophy of Sports}. \mbox{G\"oteborg} 2000

\columnbreak

\item Lars Sandman.\enspace\textit{A Good Death: On the Value of Death and Dying}. \mbox{G\"oteborg} 2001

\item Kent Gustavsson.\enspace\textit{Emergent Consciousness: Themes in C.~D.~Broad's Philosophy of Mind}. \mbox{G\"oteborg} 2002

\item Frank Lorentzon.\enspace\negthinspace\negthinspace\textit{Fri Vilja?} \mbox{G\"oteborg} 2002

\item Jan Lif.\enspace\textit{Can a Consequentialist be a real friend? (Who cares?)} \mbox{G\"oteborg} 2003

\item Fredrik Sundqvist.\enspace\textit{Perceptual Dynamics: Theoretical foundations and philosophical implications of gestalt psychology}. \mbox{G\"oteborg} 2003

\item Jonas Gren.\enspace\textit{Applying utilitarianism: The problem of practical action-guidance}. \mbox{G\"oteborg} 2004

\item Niklas Juth.\enspace\textit{Genetic Information Values and Rights: The Morality of Presymptomatic Genetic Testing}. \mbox{G\"oteborg} 2005

\item Susanna Radovic.\enspace\textit{Introspecting Representations}. \mbox{G\"oteborg} 2005

\item Petra Andersson.\enspace\textit{Humanity and nature:\\ Towards a consistent holistic environmental ethics}. \mbox{G\"oteborg} 2007

\item Jan Alm\"ang.\enspace\textit{Intentionality and intersubjectivity}. \mbox{G\"oteborg} 2007

\item Alexander Alm\'{e}r.\enspace\textit{Naturalising intentionality: Inquiries into realism \& relativism}. \mbox{G\"oteborg} 2007

\item Kristoffer Ahlstr\"om.\enspace\textit{Constructive Analysis: A Study in Epistemological Methodology}. \mbox{G\"oteborg} 2007

\pagebreak

\item Ragnar Franc\'{e}n.\enspace\textit{Metaethical Relativism: Against the Single Analysis Assumption}. \mbox{G\"oteborg} 2007

\item Joakim Sandberg.\enspace\textit{The Ethics of Investing: Making Money or Making a Difference?} \mbox{G\"oteborg} 2008

\item Christer Svennerlind.\enspace\textit{Moderate Nominalism and Moderate Realism}. \mbox{G\"oteborg} 2008

\item J\"orgen Sj\"ogren.\enspace\textit{Concept Formation in Mathematics}. \mbox{G\"oteborg} 2011

\item Peter Georgsson.\enspace\textit{Metaphor and Indirect Communication in Nietzsche}. \mbox{G\"oteborg} 2014

\item Martin Kas\aa{}.\enspace\textit{Truth and Proof in the Long Run: Essays on Trial-and-Error Logics}. \mbox{G\"oteborg} 2017

\item Rasmus Blanck.\enspace\textit{Contributions to the Meta-\\mathematics of Arithmetic:~Fixed Points, Independence, and Flexibility}. \mbox{G\"oteborg} 2017

\item Martin Filin Karlsson.\enspace\textit{All There Is: On the Semantics of Quantification over Absolutely Everything}. \mbox{G\"oteborg} 2018

\item Paul Kindvall Gorbow.\enspace\textit{Self-similarity in the foundations}. \mbox{G\"oteborg} 2018

\item Marco Tiozzo.\enspace\textit{Moral Disagreement and the Significance of Higher-Order Evidence}. \mbox{G\"oteborg} 2018

\item Ylwa Sj\"olin Wirling.\enspace\textit{Modal Empiricism Made Difficult}. \mbox{G\"oteborg} 2019

\item Alva Str\aa{}ge.\enspace\textit{Minds, Brains and Desert: On the relevance of neuroscience for retributive punishment}. \mbox{G\"oteborg} 2019

\item Stellan Petersson.\enspace\textit{Disarming Context Dependence: A Formal Inquiry into Indexicalism and Truth-Conditional Pragmatics}. \mbox{G\"oteborg} 2019

\item Thomas Hartvigsson.\enspace\textit{Explorations of the Relationship Between the Right to Make Decisions and Moral Responsibility in Healthcare}. \mbox{G\"oteborg} 2020

\item Alexander Andersson.\enspace\textit{Giving Executives Their Due: Just Pay, Desert, and Equality}. \mbox{G\"oteborg} 2021

\item Leila El-Alti.\enspace\textit{ Confluence and Divergence of Emancipatory Healthcare Ideals and Psychiatric Contextual Challenges}. \mbox{G\"oteborg} 2022

\item Richard End\"orfer.\enspace\textit{Weapons of Mass Destruction: Financial Crises from a Philosophical Perspective}. \mbox{G\"oteborg} 2022

\item Dorna Behdadi.\enspace\textit{Nonhuman Moral Agency: A Practice-Focused Exploration of Moral Agency in Nonhuman Animals and Artificial Intelligence}. \mbox{G\"oteborg} 2023

\item Paiman Karimi.\enspace\textit{Relaxing Normativity: Essays on Relaxed Approaches to Realism about Normativity}. \mbox{G\"oteborg} 2023
\end{Volumes}
\end{multicols*}


\end{document}
